% Created 2014-04-27 Sun 17:41
\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{soul}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{latexsym}
\usepackage{amssymb}
\usepackage{enumitem}
\setlist{nolistsep}
\setlist[itemize,2]{label={$\circ$}}
\setlist[itemize,3]{label={--}}
\usepackage[colorlinks=true, urlcolor=blue]{hyperref}
\tolerance=1000
\usepackage[margin=1.0in]{geometry}
\providecommand{\alert}[1]{\textbf{#1}}

%\usepackage[tiny]{titlesec} Screws up at \begin{center} w/ heading inside.
\makeatother

\title{Trisdan Leyson}
\author{Programmer, Software Engineer, Writer, Tutor}
\date{\today}
\hypersetup{
  pdfkeywords={},
  pdfsubject={},
  pdfcreator={Emacs Org-mode version 7.9.3f}}

\begin{document}

\maketitle

%\setcounter{tocdepth}{3}
%\tableofcontents
%\vspace*{1cm}
\begin{center}
\section*{Contact Information}
\label{sec-1}
12266 Regent Way\\
PO Box 1033\\
Oregon House, CA 95962\\
\textbf{trisdan.leyson@gmail.com}\\
\textbf{(530) 692-9040}\\
\end{center}
\section*{Education}
\label{sec-2}

\begin{itemize}
\item \textbf{Bachelor of Science, Computer Science. University of California, Davis.}
\begin{itemize}
\item In-progress; expected completion 8/2014.
\item GPA: 3.27
\end{itemize}
\item \textbf{Associate of Arts, Arts and Humanities. Yuba College.}
\begin{itemize}
\item Completed 2011.
\item GPA: 3.7
\end{itemize}
\end{itemize}
\section*{Skills}
\label{sec-3}
\subsection*{Programming Languages}
\label{sec-3-1}

\begin{itemize}
\item Most experience with Python, Java, C++.
\item Some experience with Clojure, C, Ruby, Javascript.
\item Brief exposure to Common Lisp, Prolog, JR.
\end{itemize}
\subsection*{Other technologies}
\label{sec-3-2}

\begin{itemize}
\item Working knowledge of HTML, CSS.
\item Working knowledge of Emacs, some Emacs Lisp.
\item Basic knowledge of Git and GitHub.
\item Working knowledge of Unix, Linux, and Microsoft Windows.
\end{itemize}
\subsection*{Other}
\label{sec-3-3}

\begin{itemize}
\item Proficient writer; maintain a technical blog, \textit{The Poetry of Computer Science} (\href{http://porgionesanke.wordpress.com}{porgionesanke.wordpress.com}).
\item Some knowledge of the Spanish and Japanese languages.
\end{itemize}
\section*{Selected Projects}
\label{sec-4}

\begin{itemize}
\item \textbf{Compiler for the Cool Programming Language}
\begin{itemize}
\item Implemented lexing and semantic analysis (type checking) phases.
\item \textbf{Tools}: C++, Flex, make, SPIM and MIPS.
\item \textbf{Skills}: Regular expressions, object-oriented design, type systems.
\end{itemize}
\item \textbf{Robot arm control system}
\begin{itemize}
\item Aided in designing, and implemented, an object-oriented interface.
\item \textbf{Tools}: C++.
\item \textbf{Skills}: Low-level programming, object-oriented design.
\end{itemize}
\item \textbf{Sound Change Modeler}
\begin{itemize}
\item Code at \href{https://github.com/tsleyson/PySounds2}{https://github.com/tsleyson/PySounds2}.
\item \textbf{Tools}: Python.
\item \textbf{Skills}: Regular expressions, scripting, GUIs (TKinter), Unicode.
\end{itemize}
\item \textbf{Document preparer for Amazon Kindle publishing}
\begin{itemize}
\item Code at \href{https://github.com/tsleyson/kindle_pub_formatter}{https://github.com/tsleyson/kindle\_pub\_formatter}.
\item \textbf{Tools}: Clojure, HTML, Emacs Lisp, JSON.
\item \textbf{Skills}: HTML, Cascading Style Sheets, Unicode.
\end{itemize}
\end{itemize}
\section*{Employment History}
\label{sec-5}
\subsection*{January 2014–}
\label{sec-5-1}

\begin{itemize}
\item \textbf{Yuba College Writing and Language Development Center.}
\item \textbf{Position}: English and ESL Tutor
\item \textbf{Duties}:
\begin{itemize}
\item Worked closely with students to refine language, analytical, and 
      rhetorical skills.
\item Interpreted instructor comments and assignments and communicated
      this understanding to students.
\item Kept careful records of activities within the center using the
      AccuTrack and TutorTrac systems.
\item Modeled good student behavior.
\item Created a tutorial for students to learn to use the 
      account-linking features of their Yuba College campus email.
      (Available at \href{tsleyson.github.io/WLDC-email-forward/index.html}{tsleyson.github.io/WLDC-email-forward/index.html}.)
\end{itemize}
\item \textbf{Reason for leaving}: Time-limited position.
\end{itemize}
\subsection*{June 2011–August 2013}
\label{sec-5-2}

\begin{itemize}
\item Full-time student, University of California, Davis.
\end{itemize}
\subsection*{January 2009–May 2011}
\label{sec-5-3}

\begin{itemize}
\item \textbf{Yuba College Writing and Language Development Center}
\item \textbf{Position}: English and ESL Tutor
\item \textbf{Duties}: See above.
\item \textbf{Reason for leaving}: Left to become full-time student at UC Davis.
\end{itemize}
\subsection*{January 2007–May 2011}
\label{sec-5-4}

\begin{itemize}
\item Full-time student, Yuba Community College.
\end{itemize}
\section*{References}
\label{sec-6}
\subsection*{Rosemary McKeever}
\label{sec-6-1}

\begin{itemize}
\item Relationship: Former supervisor.
\item Organization: Yuba College Writing and Language Development Center.
\item Title: Instructional Associate.
\item Email: rmckeeve@yccd.edu
\end{itemize}
\subsection*{Shawn Frederking}
\label{sec-6-2}

\begin{itemize}
\item Relationship: Former supervisor.
\item Organization: Yuba College Writing and Language Development Center,
    Yuba College English Department.
\item Title: Associate Professor of English.
\item Email: sfrederk@yccd.edu
\end{itemize}

\end{document}
